---
title: "R Notebook"
output: html_notebook
---

# Package Setup 

```{r load packages}
library(tidyverse)
library(janitor)
library(tidycensus)
library(reticulate)
```
# Peer States Prep
```{r}
#making the peer states df that can be joined to other dfs
states <- c('California', 'Colorado', 'Florida', 'Georgia', 'Illinois', 'New York', 'North Carolina', 'Ohio', 'Pennsylvania', 'Virginia', 'Washington')

state_short <- c('CA', 'CO', 'FL', 'GA', 'IL', 'NY', 'NC', 'OH', 'PA', 'VA', 'WA')

peer <- c('Y', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y', 'Y')

states <- data.frame(states, state_short, peer)

```



# Aging Data 

## Population Projections

```{r}
## This is complete

#reading in the CSV downloaded from the state demographer. Keeping only relevant data
pop_proj <- read_csv("raw_data/Aging/2018allcntyindage.csv") %>% 
  mutate(age_keeps = case_when(
    age_in_yrs_num %>% between(0,17) ~ "Keep",
    age_in_yrs_num %>% between(18,64) ~ "Keep",
    age_in_yrs_num %>% between(65,95) ~ "Keep",
    TRUE ~ "Remove"
  )) %>%
  filter(age_keeps == "Keep") %>%
  write_rds("clean_data/Aging/pop_proj_data.rds")

```
## Diabetes Data
```{r}
## This is complete

#Starting with the county level -- these do not have age breakdowns
#reading in the CSV from the CDC.Skipping the first two rows as they do not contain any relevant information
diabetes_stats_county <- read_csv("raw_data/Aging/DiabetesAtlasCountyData.csv", skip = 2) %>%
  write_rds("clean_data/Aging/diabetes_county_stats.rds")

#Moving on to Texas level data -- these have age breakdowns
#make sure to only keep data after 2012
#same process as above, reading in the CSV and skipping the first two rows. This is 75+ only
diabetes_stats_TX_75_raw <- read_csv("raw_data/Aging/DiabetesAtlasData75+.csv", skip = 2)%>%
  write_rds("clean_data/Aging/diabetes_tx_75+_stats.rds")

#same process as above, reading in the CSV and skipping the first two rows. This is 65-74 only
diabetes_stats_TX_65_raw <- read_csv("raw_data/Aging/DiabetesAtlasData65-74.csv", skip = 2) %>%
  write_rds("clean_data/Aging/diabetes_tx_65-74_stats.rds")
```


## Physical Inactivity Data
```{r}
## This is complete

#reading in the CSV from America's health rankings and keeping the relevant information
physicial_inactivity <- read_csv("raw_data/Aging/2019-Senior_TX.csv") %>%
  clean_names() %>%
  filter(`measure_name` == "Physical Inactivity - Ages 65+") %>%
  write_rds('clean_data/Aging/physical_inactivity_data.rds')
```

## Social Isolation Data
```{r}
## This is complete

#reading in the CSV. I'll keep all the records for social isolation from all the different states
social_iso <- read_csv("raw_data/Aging/2020-Senior.csv") %>%
  clean_names() %>%
  filter(`measure_name` == "Risk of Social Isolation - Ages 65+") %>%
  merge(x=social_iso, y=states, by.x='state_name', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Aging/social_iso_data.rds')
```
## Mental Health Data
```{r}
## This is complete

#reading in the CSV. I'll keep all the records for mental health from all the different states
mental_health <- read_csv("raw_data/Aging/2020-Senior.csv") %>%
  clean_names() %>%
  filter(`measure_name` == "Frequent Mental Distress - Ages 65+") %>%
  merge(x=mental_health, y=states, by.x='state_name', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Aging/mental_health_data.rds')
```
## Alzheimer’s 
```{r}
## This is complete

#reading in CSV and saving the data
alh_data <- read_csv("raw_data/Aging/Data Table.csv")%>%
  clean_names() %>%
  merge(x=alh_data, y=states, by.x='state', by.y='state_short', all.x = TRUE) %>%
  write_rds('clean_data/Aging/alzheimers_data.rds')
```
## Primary Care Access
```{r}
## This is complete

#reading in the CSV. I'll keep all the records for health providers from all the different states
dedi_health <- read_csv("raw_data/Aging/2020-Senior.csv") %>%
 clean_names() %>%
  filter(`measure_name`=="Dedicated Health Care Provider - Ages 65+") %>%
  merge(x=dedi_health, y=states, by.x='state_name', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Aging/dedicated_health_provider_data.rds')
```
## Immunization Rates
```{r}
## This is complete

#reading in the CSV. I'll keep all the records for immunization rates from all the different states
imm_rates <- read_csv("raw_data/Aging/2020-Senior.csv") %>% 
  clean_names() %>%
  filter(`measure_name` == "Immunizations - Senior")%>%
  merge(x=imm_rates, y=states, by.x='state_name', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Aging/immunization_rates_data.rds')
```

## Nursing Home Quality
```{r}
## This is complete

#reading in the CSV. I'll keep all the records for nursing home quality from all the different states
nursing_homes <- read_csv("raw_data/Aging/2020-Senior.csv") %>%
  clean_names() %>%
  filter(`measure_name` == "Nursing Home Quality")  %>%
  merge(x=nursing_homes, y=states, by.x='state_name', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Aging/nursing_homes_data.rds')
```

# Childhood Data
## Obesity and Overweight
```{r}
## This is complete

# Starting with obesity and overweight data for children across all states
#reading in the data and only keeping childhood obesity and overweight rates
chd_obes <- read_csv('raw_data/Children/2019-HWC.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Overweight or Obesity-Youth") %>%
  merge(x=chd_obes, y=states, by.x='state_name', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Children/childhood_obesity_data.rds')

#reading in the data and only keeping childhood obesity and overweight rates for children in WIC between the ages of 2-4
wic_obes <- read_csv('raw_data/Children/ExportCSV.csv') %>%
  clean_names() %>%
  merge(x=wic_obes, y=states, by.x='location_desc', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Children/wic_obesity_data.rds')
```
## Physical Inactivity 
```{r}
## This is complete

##reading data for youth inactivity
chld_inac <- read_csv('raw_data/Children/child_inactivity.csv') %>%
  clean_names() %>%
  write_rds('clean_data/Children/child_inactivity_data.rds')
```
## Smoking
```{r}
## This is complete

#reading in the data for youth smoking rates

#this is electronic vape usage
child_vape_use <- read_csv('raw_data/Children/current_vape_use.csv') %>%
  clean_names() %>%
  merge(x=child_vape_use, y=states, by.x='location_desc', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Children/child_vape_data.rds')

#this if for any tobacco use
child_tob_use <- read_csv('raw_data/Children/current_any_tobacco_use.csv') %>%
  clean_names() %>%
  merge(x=child_tob_use, y=states, by.x='location_desc', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Children/child_tobacco_data.rds')

#this if for any tobacco usage trend
child_tob_use <- read_csv('raw_data/Children/current_any_tobacco_trend.csv') %>%
  clean_names() %>%
  write_rds('clean_data/Children/child_tobacco_trend.rds')

```

## Mental Health
```{r}
## This is complete

#reading in the mental health data
child_mental_health <- read_csv('raw_data/Children/child_mental_health.csv') %>%
  clean_names() %>%
  write_rds('clean_data/Children/child_mental_health_data.rds')
```
## Suicide Data
```{r}
## This is complete

## keeping on teen suicide data for Texas and the US, first for 2019
teen_suici_19 <- read_csv('raw_data/Children/2019-HWC.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Teen Suicide") %>%
  filter((`state_name` == "Texas") |  (`state_name` == "United States"))

#2018
teen_suici_18 <- read_csv('raw_data/Children/2018-HWC.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Teen Suicide") %>%
  filter((`state_name` == "Texas") |  (`state_name` == "United States"))

#2016
teen_suici_16 <- read_csv('raw_data/Children/2016-HWC.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Teen Suicide") %>%
  filter((`state_name` == "Texas") |  (`state_name` == "United States"))


teen_suici <- rbind(teen_suici_19, teen_suici_18, teen_suici_16) %>%
  write_rds('clean_data/Children/teen_suicide_data.rds')
```
## Childhood uninsured rates
```{r}
## This is complete

child_inse <- read_csv('raw_data/Children/SAHIE_28SEP20_15_39_23_13.csv') %>%
  clean_names() %>%
  merge(x=child_inse, y=states, by.x='name', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Children/child_uninsured_data.rds')
```
## Access to primary care
```{r}
## This is complete

chd_pc <- read_csv('raw_data/Children/2019-HWC.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Clinical Care-Children") %>%
  merge(x=chd_pc, y=states, by.x='state_name', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Children/childhood_primary_care.rds')
```

# Working Age Data

## phyisical inactivity 
```{r}
## This is NOT complete

working_activity <- read_csv('raw_data/Working Age/Physical Activity.csv') %>%
  clean_names() %>%
  write_rds('clean_data/Working Age/working_activity.rds')
```

## Mental Health
```{r}
## This is complete

mental_2019 <- read_csv('raw_data/Working Age/2019-Annual.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Frequent Mental Distress") %>%
  filter((`state_name` == "Texas") |  (`state_name` == "United States"))
  
mental_2018 <- read_csv('raw_data/Working Age/2018-Annual.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Frequent Mental Distress") %>%
  filter((`state_name` == "Texas") |  (`state_name` == "United States"))

mental_2017 <- read_csv('raw_data/Working Age/2017-Annual.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Frequent Mental Distress") %>%
  filter((`state_name` == "Texas") |  (`state_name` == "United States"))

mental_2016 <- read_csv('raw_data/Working Age/2016-Annual.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Frequent Mental Distress") %>%
  filter((`state_name` == "Texas") |  (`state_name` == "United States"))

mental_2015 <- read_csv('raw_data/Working Age/2015-Annual.csv') %>%
  clean_names() %>%
  filter(`measure_name` == "Frequent Mental Distress") %>%
  filter((`state_name` == "Texas") |  (`state_name` == "United States"))

mental_health_working <- rbind(mental_2019, mental_2018, mental_2017, mental_2016, mental_2015) %>%
  write_rds('clean_data/Working Age/mental_health_data.rds')
```


## Cardiovascular Health
```{r}
## This is complete

card_health = read_csv('raw_data/Working Age/report.csv') %>%
  clean_names() %>%
  write_rds('clean_data/Working Age/cardio_health.rds')

```

## Adult uninsured rates
```{r}
## This is complete

adul_inse <- read_csv('raw_data/Working Age/SAHIE_28SEP20_16_32_06_79.csv') %>%
  clean_names() %>%
  merge(x=adul_inse, y=states, by.x='name', by.y='states', all.x = TRUE) %>%
  write_rds('clean_data/Working Age/adult_uninsured_data.rds')
```